### 2024-02-09 docs/index.qmd
Add templates for executive summaries
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

::: {.content-visible when-profile="seasonality"}

Exploration on seasonality is done on monthly data with a first-order difference

>>>>

```{r init}

options(scipen = 999)

```

::: {.content-visible when-meta="in.report"}
{{< include exec-summary/report.qmd >}}
:::

::: {.content-visible when-profile="descriptive"}
{{< include exec-summary/descriptive.qmd >}}
:::

::: {.content-visible when-profile="arima"}
{{< include exec-summary/arima.qmd >}}
:::

::: {.content-visible when-profile="seasonality"}
{{< include exec-summary/seasonality.qmd >}}
:::

::: {.content-visible when-profile="spectral"}
{{< include exec-summary/spectral.qmd >}}
:::

::: {.content-visible when-meta="in.report"}

## Contents

- @sec-descriptive contains a descriptive explanation of the dataset
- @sec-seasonality reports exploration of seasonality on detrended data
- @sec-arima showcases results obtained from ARIMA models
- @sec-spectral outlines the decomposed time series using singular-spectrum analysis

### 2024-02-09 docs/results/descriptive.qmd
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

options(digits = 2)

@@

# Results

@@

In this section,

```{r}
#| tbl-cap: Mean difference of all metrics before and during COVID-19

@@

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

### Paired plot of all metrics for each medication group

@@

@@

@@

## Descriptive analysis of the deseasonalized data

@@

tar_read(plt_decom_ts_day_1.week_classic_n_claim)
tar_read(plt_decom_ts_day_1.week_classic_claim2patient)
tar_read(plt_decom_ts_day_1.week_classic_eigen)

@@

@@

tar_read(plt_decom_ts_week_1.month_classic_n_claim)
tar_read(plt_decom_ts_week_1.month_classic_claim2patient)
tar_read(plt_decom_ts_week_1.month_classic_eigen)

@@

@@

tar_read(plt_decom_ts_month_1.year_classic_n_claim)
tar_read(plt_decom_ts_month_1.year_classic_claim2patient)
tar_read(plt_decom_ts_month_1.year_classic_eigen)

@@

>>>>

options(digits = 2, scipen = 999)

@@

# Results on descriptive statistics {#sec-descriptive}

@@

```{r tbl-mean-diff}
#| tbl-cap: Mean difference of all metrics before and during COVID-19

@@

\uselandscape

:::: {.content-hidden when-meta="in.report"}

### Paired plot of all metrics for each medication group {#sec-pair-plot}

@@

::: {.content-visible when-profile="descriptive"}

@@

:::

@@

::::

## Descriptive analysis of the decomposed data {#sec-decom-classic-stl}

### Decomposed time-series on a daily interval

@@

tar_read(plt_decom_ts_day_1.week_classic_n_claim)
tar_read(plt_decom_ts_day_1.week_classic_eigen)

@@

### Decomposed time-series on a weekly interval

@@

tar_read(plt_decom_ts_week_1.month_classic_n_claim)
tar_read(plt_decom_ts_week_1.month_classic_eigen)

@@

### Decomposed time-series on a monthly interval

@@

tar_read(plt_decom_ts_month_1.year_classic_n_claim)
tar_read(plt_decom_ts_month_1.year_classic_eigen)

@@

\normalpapersize

### 2024-02-09 docs/results/spectral.qmd
Increase the number of clusters when grouping the oscillating functions #6 CU-86cuhtqmg
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

---
knitr:
  opts_chunk:
    fig.width: 14
    fig.height: 8
---

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

@@

pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)

@@

  tbl   <- res %>%
    tseries::pp.test() %>%
    broom::tidy() %>%
    subset(select = c("statistic", "p.value", "method")) %>%
    set_colnames(c("stat", "p", "method")) %>%
    inset(c("stat2", "p2", "method2"), value = normality) %>%
    tibble::add_column("group" = group, .before = 1) %>%
    dplyr::mutate(
      "mean"   = mean(res),
      "median" = median(res),
      "sd"     = sd(res),
      "IQR"    = IQR(res)
    )

@@

# Results

@@

tar_read(mod_ssa_n_claim) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

tar_read(mod_ssa_claim2patient) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

@@

tar_read(mod_ssa_eigen) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

@@

## Reconstructed plots

@@

### Medication claim to patient ratio

>>>>

---
knitr:
  opts_chunk:
    fig.width: 18
    fig.height: 12
---

@@

pkgs <- c("magrittr", "targets", "kableExtra")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2, scipen = 999)

prettyRound <- function(x, ...) {
  x %<>% round(...) %>% {ifelse(. == 0, "<0.001", as.character(.))}
}

@@

  tbl <- res %>%
    tseries::pp.test() %>%
    broom::tidy() %>%
    subset(select = c("statistic", "p.value", "method")) %>%
    set_colnames(c("stat", "p", "method")) %>%
    inset(c("stat2", "p2", "method2"), value = normality) %>%
    tibble::add_column("group" = group, .before = 1) %>%
    dplyr::mutate(
      "Unit Root" = sprintf("%s (p %s)", round(stat, 2), prettyRound(p, 3)),
      "Normality" = sprintf("%s (p %s)", round(stat2, 2), prettyRound(p2, 3)),
      "Mean"   = mean(res),
      "SD"     = sd(res),
      "Median" = median(res),
      "IQR"    = IQR(res)
    ) %>%
    subset(select = -c(stat:method2)) %>%
    dplyr::rename("ATCC Group" = group)

@@

\normalpapersize

# Results on singular spectrum analysis {#sec-spectral}

## Trend evaluation

```{r tbl-trend}
#| tbl-cap: Trend of medication uses alongside its measure of relative importance

fnote <- "The statistics were obtained from Mann-Kendall trend test, where positive result signifies a positive slope"

tar_read(decom_ssa) %>%
  subset(.$component %in% c("Original", "Trend") & .$metric != "claim2patient") %>%
  tibble::tibble() %>%
  dplyr::group_by(metric, group, component) %>%
  dplyr::group_modify(~trend::mk.test(.x$value) %>% broom::tidy()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    "Mann-Kendall" = sprintf(
      "%s (p %s)", prettyRound(statistic, 2), prettyRound(p.value, 3)
    )
  ) %>%
  subset(select = -c(statistic:alternative)) %>%
  tidyr::pivot_wider(names_from = metric, values_from = `Mann-Kendall`) %>%
  tidyr::pivot_wider(names_from = component, values_from = eigen:n_claim) %>%
  set_colnames(c("ATCC Group", rep(c("Original", "Trend"), 2))) %>%
  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = "repeat_header") %>%
  kableExtra::add_header_above(c(" " = 1, "Eigenvector Centrality" = 2, "Medication Claims" = 2)) %>%
  kableExtra::add_footnote(fnote, notation = "none")

\uselandscape

@@

```{r tbl-resid-n-claim}
#| tbl-cap: Residuals analysis for unit-root and normality test for the decomposition model of number of claims

tar_read(mod_ssa_n_claim) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = "repeat_header", font_size = 8)

@@

```{r tbl-resid-eigen}
#| tbl-cap: Residuals analysis for unit-root and normality test for the decomposition model of relative importance

tar_read(mod_ssa_eigen) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = "repeat_header", font_size = 8)

@@

## Reconstructed plots {#sec-recon}

@@

::: {.content-visible when-profile="spectral"}
